Extension of the approximate static condensation method for multi-material diffusion problems to 3D

### 2019-08-07 3d/asc3d.tex
Add more comments

\subsection{Interface without multi-material faces}

\AZ{TBA\dots}

\subsection{Interface with multi-material faces}

\AZ{TBA\dots}

@@

>>>>

\subsection{Constant concentration on multi-material faces}

\AZ{TBA: $p = 1$ (voronoi sandwich mesh) and $p = 2\,z + 1$ (square)}

\subsection{General example: planar sandwich}

\AZ{TBA: high-contrast $k$, sequence of voronoi and brick meshes (skewed parallel interfaces), compare with homo, plot fluxes}

@@

\AZ{Add building / running instructions as an appendix}
